Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2025-01-03 presentation/backup.tex
Final presentation

>>>>

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.65\columnwidth]{halfway-g1}
    \caption{Group 1 neutron flux distribution with Rod 1 inserted by 27.5 inches.}
    \label{fig:halfway-g1}
  \end{figure}
\end{frame}

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.65\columnwidth]{halfway-g8}
    \caption{Group 8 neutron flux distribution with Rod 1 inserted by 27.5 inches.}
    \label{fig:halfway-g8}
  \end{figure}
\end{frame}

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.65\columnwidth]{inserted-g1}
    \caption{Group 1 neutron flux distribution with Rod 1 inserted by 51 inches.}
    \label{fig:inserted-g1}
  \end{figure}
\end{frame}

\begin{frame}[noframenumbering]
  \begin{figure}[t]
    \centering
    \includegraphics[width=.65\columnwidth]{inserted-g8}
    \caption{Group 8 neutron flux distribution with Rod 1 inserted by 51 inches.}
    \label{fig:inserted-g8}
  \end{figure}
\end{frame}
